TITLE??

### 2018-04-30 paper.Rmd
Change to tech-college grouping, use multinomial regression

@@

<!-- TABLE: High-tech and low-tech industry sectors -->
\begingroup\setstretch{1.0}
\input{tex/top_bottom_tech_ind_manual.tex}
\endgroup

>>>>

\newcommand{\inputtable}[1]{
  \begingroup\setstretch{1.0}
  \input{#1}
  \endgroup
}

@@

<!-- TABLE: High-tech and low-tech industry sectors -->
<!-- \begingroup\setstretch{1.0} -->
<!-- \input{tex/top_bottom_tech_ind_manual.tex} -->
<!-- \endgroup -->

\inputtable{tex/top_bottom_tech_ind_manual.tex}
